\documentclass[a4paper,11pt]{article}
\usepackage[margin=1.5cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fontawesome5}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{
    colorlinks=true,
    urlcolor=linkcolour,
    linkcolor=linkcolour
}
\pagestyle{empty}
\titleformat{\section}
{\large\bfseries}
{}
{0em}
{}
[\titlerule]
\titlespacing{\section}{0pt}{10pt}{6pt}
\begin{document}
\begin{center}
    {\LARGE \textbf{Roman Suhanov}} \\[6pt]
    Minsk, Belarus \\[4pt]
    \href{https://github.com/rmkaaaa}{\faGithub\ rmkaaaa}
    \quad | \quad
    \href{https://www.kaggle.com/rmkaaaa}{Kaggle}
    \quad | \quad
    \href{mailto:romansuhanov1111@gmail.com}{\faEnvelope\ romansuhanov1111@gmail.com}
    \\[4pt]
    \href{https://www.linkedin.com/in/роман-суханов-0486473ba/}{\faLinkedin\ LinkedIn}
    \quad | \quad
    \href{https://t.me/rmkaaaaaa}{\faTelegram\ @rmkaaaaaa}
\end{center}
\section{Summary}
Computer Science student at Belarusian State University (FAMCS), focused on Machine Learning and data analysis. 
Experienced in applying machine learning algorithms, performing exploratory data analysis (EDA), and building gradient boosting 
ensembles. Actively participating in Kaggle competitions and improving model performance through experimentation. 
Also build Telegram bots and AI automation pipelines. Interested in Machine Learning internships.
\section{Projects}
\textbf{F1 Pit Stop Strategy Prediction}
\hfill
\href{https://github.com/rmkaaaa}{GitHub}
\begin{itemize}[leftmargin=1.2em, itemsep=2pt]
    \item Built a binary classification model to predict pit stop decisions during Formula 1 races.
    \item Engineered domain-specific features (tyre degradation, race progress, pit-pressure indicators).
    \item Trained and tuned gradient boosting models (XGBoost, LightGBM, CatBoost) with StratifiedKFold cross-validation.
    \item Combined models via weighted blending and Logistic Regression stacking, evaluated with ROC AUC.
    \item Performed hyperparameter optimization (grid search and Optuna).
\end{itemize}
\vspace{4pt}
\textbf{Telegram Bots \& AI Automation}
\begin{itemize}[leftmargin=1.2em, itemsep=2pt]
    \item Developed Telegram bots in Python (aiogram) integrating LLMs for conversational features.
    \item Built AI automation workflows with n8n to connect LLMs, APIs, and external services.
    \item Worked with local LLMs through Ollama for offline inference.
    \item Containerized applications with Docker for reproducible deployment.
\end{itemize}
\vspace{4pt}
\textbf{Machine Learning Coursework}
\hfill
\href{https://github.com/rmkaaaa/ml-course-homework}{GitHub}
\begin{itemize}[leftmargin=1.2em, itemsep=2pt]
    \item Performed exploratory data analysis (EDA) and data preprocessing.
    \item Implemented and evaluated multiple ML models: KNN, Linear Regression, Logistic Regression, Naive Bayes, Decision Trees, SVM, Random Forest, Gradient Boosting.
    \item Compared model performance and selected appropriate approaches for different tasks.
    \item Visualized data using Matplotlib and Seaborn.
\end{itemize}
\section{Kaggle Experience}
\begin{itemize}[leftmargin=1.2em, itemsep=2pt]
    \item Active participant in Kaggle competitions.
    \item Ranked 789/4890 (Top 16\%) in House Prices: Advanced Regression Techniques competition using Logistic Regression.
    \item Ranked 885/4317 (Top 21\%) in Playground Series S6E1 using Logistic Regression.
    \item Ranked 1054/4315 (Top 25\%) in Playground Series S6E4 using model stacking (CatBoost, LightGBM, XGBoost, SVM) to improve accuracy and model diversity.
\end{itemize}
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2025 -- Present & 
\textbf{Belarusian State University} \\
& Faculty of Applied Mathematics and Computer Science \\
& B.S. in Applied Informatics \\
\end{tabularx}
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming Languages & C++, C\#, Python \\
Machine Learning & KNN, Linear Regression, Logistic Regression, Naive Bayes, Decision Trees, SVM, Random Forest, Gradient Boosting (XGBoost, LightGBM, CatBoost) \\
Data \& Libraries & NumPy, pandas, scikit-learn, Optuna \\
Visualization & Matplotlib, Seaborn \\
Tools \& Automation & Git, GitHub, Docker, n8n, Ollama, aiogram, Qt (beginner) \\
IDEs & PyCharm, Rider, CLion, Visual Studio, VS Code \\
Concepts & EDA, data preprocessing, model evaluation, ensemble methods (stacking, blending), cross-validation, hyperparameter tuning, feature engineering \\
\end{tabularx}
\section{Achievements}
\begin{itemize}[leftmargin=1.2em, itemsep=2pt]
    \item Participant in regional olympiads in mathematics and physics
\end{itemize}
\section{Languages}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Russian & Native \\
Belarusian & Native \\
English & B1 (Intermediate) \\
\end{tabularx}
\end{document}
